---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# polyread

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/polyread)](https://CRAN.R-project.org/package=polyread)
<!-- badges: end -->

The goal of polyread is to read Polygon Filter File Format (`.poly`) files (which are defined [here](https://wiki.openstreetmap.org/wiki/Osmosis/Polygon_Filter_File_Format)), and convert them to [`sfc`](https://r-spatial.github.io/sf/reference/sfc.html) format.

## Installation

You can install the development version of `polyread` with:

```{r, eval = FALSE}
remotes::install_github("agila5/polyread")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(polyread)

## basic example code: read a poly file and convert to MULTIPOLYGON
africa_url <- "http://download.openstreetmap.fr/polygons/africa.poly"
africa_con <- url(africa_url)
africa_poly <- readLines(africa_con); close(africa_con) # don't forget to close the connection
(africa_multipolygon <- convert_poly_to_sfc(africa_poly))
```

A map: 

```{r}
italy_con <- url("http://download.openstreetmap.fr/polygons/europe/italy.poly")
italy_poly <- readLines(italy_con); close(italy_con)

italy_multipolygon <- convert_poly_to_sfc(italy_poly)
mapview::mapview(italy_multipolygon)
```

## Code of Conduct

Please note that the polyread project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

